---
title: "Midfield Analysis"
author: "Molly McCann, Sarah Cernugel, Taylor Hill"
date: "2024-10-01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(ggplot2)
library(ggimage)
library(rsvg)
library(tidyverse)
library(httr)
library(rvest)
library(jsonlite)
library(reshape)

mid_final <- read.csv("~/Downloads/DataAquisition/Project/final_data.csv")
crest <- read.csv("~/Downloads/DataAquisition/Project/crest.csv")
```


## Hypothesis Testing 

# Manchester City 

H0: arsenal avg midfield pass = manchester city avg midfield pass
HA: arsenal avg midfield pass > manchester city avg midfield pass

```{r}
mci_data <- mid_final |>
  filter(team_abbr %in% c("ARS", "MCI"))

mci_test <- t.test(
  passes ~ team_abbr, 
  data = mci_data, 
  alternative = "greater"  
)

mci_test
```
# Liverpool 

H0: arsenal avg midfield pass = liverpool avg midfield pass
HA: arsenal avg midfield pass > liverpool avg midfield pass

```{r}
liv_data <- mid_final |>
  filter(team_abbr %in% c("ARS", "LIV"))

liv_test <- t.test(
  formula =  passes ~ team_abbr, 
  data = liv_data, 
  alternative = "greater"
)

liv_test
```

# Aston Villa 

H0: arsenal avg midfield pass = aston villa avg midfield pass
HA: arsenal avg midfield pass > aston villa avg midfield pass

```{r}
avl_data <- mid_final |>
  filter(team_abbr %in% c("ARS", "AVL"))

avl_test <- t.test(
  formula =  passes ~ team_abbr, 
  data = avl_data, 
  alternative = "greater"
)

avl_test
```
# Tottenham Hotspur 

H0: arsenal avg midfield pass = tottenham avg midfield pass
HA: arsenal avg midfield pass > tottenham avg midfield pass

```{r}
tot_data <- mid_final |>
  filter(team_abbr %in% c("ARS", "TOT"))

tot_test <- t.test(
  formula =  passes ~ team_abbr, 
  data = tot_data, 
  alternative = "greater"
)

tot_test
```

# Chelsea 

H0: arsenal avg midfield pass = chelsea avg midfield pass
HA: arsenal avg midfield pass > chelsea avg midfield pass

```{r}
che_data <- mid_final |>
  filter(team_abbr %in% c("ARS", "CHE"))

che_test <- t.test(
  formula =  passes ~ team_abbr, 
  data = che_data, 
  alternative = "greater"
)

che_test
```

# Newcastle United 

H0: arsenal avg midfield pass = newccastle avg midfield pass
HA: arsenal avg midfield pass > newcastle avg midfield pass

```{r}
new_data <- mid_final |>
  filter(team_abbr %in% c("ARS", "NEW"))

new_test <- t.test(
  formula =  passes ~ team_abbr, 
  data = new_data, 
  alternative = "greater"
)

new_test
```

# Manchester United 

H0: arsenal avg midfield pass = manchester united avg midfield pass
HA: arsenal avg midfield pass > manchester united avg midfield pass

```{r}
mun_data <- mid_final |>
  filter(team_abbr %in% c("ARS", "MUN"))

mun_test <- t.test(
  formula =  passes ~ team_abbr, 
  data = mun_data, 
  alternative = "greater"
)

mun_test
```

# West Ham United 

H0: arsenal avg midfield pass = west ham united avg midfield pass
HA: arsenal avg midfield pass > west ham united avg midfield pass

```{r}
whu_data <- mid_final |>
  filter(team_abbr %in% c("ARS", "WHU"))

whu_test <- t.test(
  formula =  passes ~ team_abbr, 
  data = whu_data, 
  alternative = "greater"
)

whu_test
```

# Crystal Palace

H0: arsenal avg midfield pass = crystal palace avg midfield pass
HA: arsenal avg midfield pass > crystal palace avg midfield pass

```{r}
cry_data <- mid_final |>
  filter(team_abbr %in% c("ARS", "CRY"))

cry_test <- t.test(
  formula =  passes ~ team_abbr, 
  data = cry_data, 
  alternative = "greater"
)

cry_test
```

# Brighton & Hove Albion 

H0: arsenal avg midfield pass = brighton & hove albion avg midfield pass
HA: arsenal avg midfield pass > brighton & hove albion avg midfield pass

```{r}
bha_data <- mid_final |>
  filter(team_abbr %in% c("ARS", "BHA"))

bha_test <- t.test(
  formula =  passes ~ team_abbr, 
  data = bha_data, 
  alternative = "greater"
)

bha_test
```

# Fulham

H0: arsenal avg midfield pass = fulham avg midfield pass
HA: arsenal avg midfield pass > fulham united avg midfield pass

```{r}
ful_data <- mid_final |>
  filter(team_abbr %in% c("ARS", "FUL"))

ful_test <- t.test(
  formula =  passes ~ team_abbr, 
  data = ful_data, 
  alternative = "greater"
)

ful_test
```

# Bournemouth 

H0: arsenal avg midfield pass = bournemouth avg midfield pass
HA: arsenal avg midfield pass > bournemouth avg midfield pass

```{r}
bou_data <- mid_final |>
  filter(team_abbr %in% c("ARS", "BOU"))

bou_test <- t.test(
  formula =  passes ~ team_abbr, 
  data = bou_data, 
  alternative = "greater"
)

bou_test
```

# Wolverhampton Wanderers 

H0: arsenal avg midfield pass = wolverhampton avg midfield pass
HA: arsenal avg midfield pass > wolverhampton avg midfield pass

```{r}
wol_data <- mid_final |>
  filter(team_abbr %in% c("ARS", "WOL"))

wol_test <- t.test(
  formula =  passes ~ team_abbr, 
  data = wol_data, 
  alternative = "greater"
)

wol_test
```

# Everton 

H0: arsenal avg midfield pass = everton avg midfield pass
HA: arsenal avg midfield pass > everton avg midfield pass

```{r}
eve_data <- mid_final |>
  filter(team_abbr %in% c("ARS", "EVE"))

eve_test <- t.test(
  formula =  passes ~ team_abbr, 
  data = eve_data, 
  alternative = "greater"
)

eve_test
```

# Brentford

H0: arsenal avg midfield pass = brentford avg midfield pass
HA: arsenal avg midfield pass > brentford avg midfield pass

```{r}
bre_data <- mid_final |>
  filter(team_abbr %in% c("ARS", "BRE"))

bre_test <- t.test(
  formula =  passes ~ team_abbr, 
  data = bre_data, 
  alternative = "greater"
)

bre_test
```

# Nottingham Forest 

H0: arsenal avg midfield pass = nottingham forest avg midfield pass
HA: arsenal avg midfield pass > nottingham forest avg midfield pass

```{r}
nfo_data <- mid_final |>
  filter(team_abbr %in% c("ARS", "NFO"))

nfo_test <- t.test(
  formula =  passes ~ team_abbr, 
  data = nfo_data, 
  alternative = "greater"
)

nfo_test
```

Vizualization



## Wins

```{r}
url_1 <- "https://footballapi.pulselive.com/football/stats/ranked/teams/wins?page=0&pageSize=10&compSeasons=578&comps=1&altIds=true"
win_res1 <- GET(url_1,
    add_headers(
      "user-agent" = "Mozilla/5.0 (Macintosh; Intel Mac OS X 10_15_7) AppleWebKit/537.36 (KHTML, like Gecko) Chrome/128.0.0.0 Safari/537.36",
      "origin" = "https://www.premierleague.com",
      "referer" = "https://www.premierleague.com/"
    ))

win_cont1 <- content(win_res1, as = "text")
win_json1 <- fromJSON(win_cont1)
str(win_json1)

wins1 <- jsonlite::flatten(win_json1$stats$content)
wins1
```

```{r}
url_2 <- "https://footballapi.pulselive.com/football/stats/ranked/teams/wins?page=1&pageSize=10&compSeasons=578&comps=1&altIds=true"
win_res2 <- GET(url_2,
    add_headers(
      "user-agent" = "Mozilla/5.0 (Macintosh; Intel Mac OS X 10_15_7) AppleWebKit/537.36 (KHTML, like Gecko) Chrome/128.0.0.0 Safari/537.36",
      "origin" = "https://www.premierleague.com",
      "referer" = "https://www.premierleague.com/"
    ))

win_cont2 <- content(win_res2, as = "text")
win_json2 <- fromJSON(win_cont2)
str(win_json2)

wins2 <- jsonlite::flatten(win_json2$stats$content)
wins2
```

```{r}
df_teams <- list(wins1, wins2)
teams <- merge_recurse(df_teams)

teams <- teams %>% select(owner.name, owner.club.abbr, value)

teams <- dplyr::rename(teams, team = owner.name, team_abbr = owner.club.abbr, wins = value)
```

## Passes

```{r}
pass_url_1 <- "https://footballapi.pulselive.com/football/stats/ranked/teams/total_pass?page=0&pageSize=10&compSeasons=578&comps=1&altIds=true"
passes_res1 <- GET(pass_url_1,
    add_headers(
      "user-agent" = "Mozilla/5.0 (Macintosh; Intel Mac OS X 10_15_7) AppleWebKit/537.36 (KHTML, like Gecko) Chrome/128.0.0.0 Safari/537.36",
      "origin" = "https://www.premierleague.com",
      "referer" = "https://www.premierleague.com/"
    ))

passes_cont1 <- content(passes_res1, as = "text")
passes_json1 <- fromJSON(passes_cont1)
str(passes_json1)

passes1 <- jsonlite::flatten(passes_json1$stats$content)
passes1
```

```{r}
pass_url_2 <- "https://footballapi.pulselive.com/football/stats/ranked/teams/total_pass?page=1&pageSize=10&compSeasons=578&comps=1&altIds=true"
passes_res2 <- GET(pass_url_2,
    add_headers(
      "user-agent" = "Mozilla/5.0 (Macintosh; Intel Mac OS X 10_15_7) AppleWebKit/537.36 (KHTML, like Gecko) Chrome/128.0.0.0 Safari/537.36",
      "origin" = "https://www.premierleague.com",
      "referer" = "https://www.premierleague.com/"
    ))

passes_cont2 <- content(passes_res2, as = "text")
passes_json2 <- fromJSON(passes_cont2)
str(passes_json2)

passes2 <- jsonlite::flatten(passes_json2$stats$content)
passes2
```

```{r}
df_teams2 <- list(passes1, passes2)
teams2 <- merge_recurse(df_teams2)

teams2 <- teams2 %>% select(owner.name, value)
teams2 <- dplyr::rename(teams2, team = owner.name, passes = value)

teams <- merge(teams, teams2, by = "team", all = TRUE)
```


```{r}
plot_dat <- merge(teams, crest, by.x = "team_abbr", by.y = "Team")

ggplot(plot_dat, aes(x = wins, y = passes)) +
  geom_point() + 
  geom_image(aes(image = URL), size = 0.1) +  # Use geom_image to plot crests
  theme_minimal() +
  labs(x = "Wins", y = "Passes", title = "Wins vs Pass")
```









